---
title: "Alcohol vs Seat choice"
author: "Sarah Medina"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
 The box plot shows that the people who sit in the back consume more alcohol than the people who sit in the middle or front. Additionally, the median also demonstrates this because the median for the people who sat in the back is 2. The median for those who sat in the front is zero. Finally, the median for those who sat in the middle is one. 
  
  
### get fancy  

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```




The median for the back is 4. The median for the front is 0. The median for the middle is 1.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


We can see through the one way anova test and given the Pr value of 0.000116 indicates that there is a 0.000116 chance that all the rows will be the same. This allows us to conclude that each row will have a always have a different value for alcohol consumption. Therefore, each row is different from one another.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
.



The Three elements demonstrates the front and back are different, the middle and back are different, but the middle and front are statistically not different.



## Conclusions

The data shows that there is a statistical difference between the front and back. There is also a difference with the middle and back. However, there is no difference between the middle and front.
